Chapter 2 Draft

### 2020-04-11 Rmd/Draft.Rmd
Preparing metadata table

\blandscape

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
setwd("~/R_Projects/Reproductive Traits")
library(kableExtra)

m <- read.csv("Data/Data_processing/metadata.csv")
kable(m)
```

\elandscape

>>>>

\begin{landscape}
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
setwd("~/R_Projects/Reproductive Traits")
library(kableExtra)

m <- read.csv("Data/Data_processing/metadata.csv")
kable(m) %>%
  kable_styling(bootstrap_options = "striped", font_size = 7)
```

\end{landscape}
